\bf Landslide: Systematic Testing in 15-410 \\ User Guide

### 2018-01-09 irb/infosheet-berkeley.tex
old cleanup: irb

\title{\bf Landslide: Systematic Testing in 15-410 \\ User Study Information Sheet}
\author{Ben Blum}
\date{}
\maketitle

@@

{\em Systematic testing}, a novel technique for testing concurrent programs, offers a mechanical way to exhaustively explore large state spaces of thread interleavings.
The purpose of the study is to compare systematic testing against stress testing in the context of 15-410.
State-of-the-art systematic testing tools are fundamentally limited by exponential state space explosion: the user must manually configure the set of {\em preemption points} which define the state space in order to achieve meaningful test results within a reasonable CPU budget.
This high cognitive overhead makes such tools unsuitable for use in a classroom setting.
However, we have extended our systematic testing platform, known as Landslide, with several novel automation techniques.
We hope to show these techniques can make systematic testing just as accessible to students as conventional stress testing.
% This study will evaluate whether Landslide is useful as an educational tool.

@@

{\bf Risks.}
We expect the risks and discomfort associated with participation in this study to be no greater than those ordinarily encountered while working on 15-410 class projects.
As always with concurrent programming, it is possible to spend a lot of time looking for a bug with no meaningful result, while that time could otherwise have been spent on project implementation.
However, as Landslide is a research tool still under development, it is also possible that a bug in Landslide itself may produce a misleading error report. We expect you to protect yourself by responsibly allocating time between using Landslide and working on P2 normally. It is expected that participation in this study will require from 2 to 8 hours of active work, depending on bug-finding results.
\\

\noindent {\bf Benefits.}
Because we are providing you with a more powerful testing tool during P2 than you would normally have access to, we hope you will be able to find and fix bugs faster, resulting in a higher grade.
%\\
%
%\noindent {\bf FALL 2014 NOTE}: As this semester we are conducting a preliminary study on a ``for fun'' basis, at the end of the semester rather than during P2, there will be no impact on your grade. 15-410 staff will not accept patches based on your findings with Landslide.

@@

During this study we will collect personally identifiable information from you as follows. While you use Landslide, it will automatically record your activity in terms of commands issued, time spent running tests, bug reports, and snapshots of your code.
%We will also collect paper surveys which you will fill out while using Landslide.
Carnegie Mellon may be required to disclose personally identifiable information as required by law, regulation, subpoena or court order.
Otherwise, we will protect your confidentiality as follows:

\begin{itemize}
	\item Data collected by Landslide will be stored in AFS accessible only to Ben Blum and Garth Gibson.
	%\item Paper surveys will be stored in a locked filing cabinet accessible only to Ben Blum and Garth Gibson.
	\item Within one semester after the study, we will destroy all personally identifying information, keeping only anonymized and aggregate results.
	\item Professor Eckhardt will have access to study data only after final semester grades are submitted. Other members of course staff will never have access to study data.
		%Course staff may, however, use Landslide on your final submitted code on their own.
		Course staff will also not have access to Landslide to grade your final submission.
\end{itemize}
%
%\noindent {\bf FALL 2014 NOTE}: This semester, Landslide's automatic data collection is not implemented. We will rely on you to supply commands issued and time spent in the survey section, and to submit Landslide's bug reports and snapshots of your code in a tarball of your workspace.

\section{Your Rights}
There is no coercion or deception associated with this study.
Your participation is voluntary.
You must be 18 years of age or older to participate.
You are free to stop your participation at any point; likewise, the Principal Investigator may at his discretion remove you from the study.
Refusal to participate or discontinued participation in the study will not result in any penalty or loss of benefits or rights to which you might otherwise be entitled.
Your participation or lack thereof will have no impact in your 15-410 class grade, except as it might (hopefully) help you write better code.
\\

\noindent If you have any questions about this study, desire additional information, or wish to withdraw
your participation please contact the Principal Investigator by mail, phone or email.
If you have questions pertaining to your rights as a research participant,
or to report concerns about this study, you should contact the
Office of Research Integrity and Compliance at Carnegie Mellon University.
Email: {\tt irb-review@andrew.cmu.edu}. Phone: 412-268-1901 or 412-268-5460.

@@

\begin{itemize}
	\item {\bf Ben Blum} (Principal Investigator): Email: {\tt bblum@cs.cmu.edu}; Office: GHC 9009; Phone: 412-304-4294
	\item {\bf Garth Gibson} (Faculty Advisor): Email: {\tt garth@cs.cmu.edu}; Office: GHC 9111
	\item {\bf David Eckhardt} (Course Instructor): Email: {\tt de0u@andrew.cmu.edu}; Office: GHC 7717
\end{itemize}

>>>>

% TODO for berkeley: CS162
\newcommand\classname{CS 162}
\title{\bf Landslide: Systematic Testing in \classname \\ User Study Information Sheet}
\author{Ben Blum}
\date{}
\maketitle

@@

{\em Systematic testing}, a novel technique for testing concurrent programs, offers a mechanical way to exhaustively explore large state spaces of thread interleavings.
The purpose of the study is to compare systematic testing against stress testing in the context of \classname.
State-of-the-art systematic testing tools are fundamentally limited by exponential state space explosion: the user must manually configure the set of {\em preemption points} which define the state space in order to achieve meaningful test results within a reasonable CPU budget.
This high cognitive overhead makes such tools unsuitable for use in a classroom setting.
However, we have extended our systematic testing platform, known as Landslide, with several novel automation techniques.
We hope to show these techniques can make systematic testing just as accessible to students as conventional stress testing.
% This study will evaluate whether Landslide is useful as an educational tool.

If you agree to participate in this study, your TA/course instructor will use Landslide to debug your submitted projects, and you will receive these debugging reports either before or after the project deadline, depending on the project.
Landslide's testing results will not be used to determine your project grade.
After you have received at least one debugging report from Landslide, we will ask you to complete a brief survey that asks about your opinions of the Landslide report.
As part of this research, we (as researchers at Carnegie Mellon) will collect the debugging reports, snapshots of your code at the time the bug was found, and your survey responses.

@@

{\bf Risks.}
We expect the risks and discomfort associated with participation in this study to be no greater than those ordinarily encountered while working on \classname~class projects.
As always with concurrent programming, it is possible to spend a lot of time looking for a bug with no meaningful result, while that time could otherwise have been spent on project implementation.
However, as Landslide is a research tool still under development, it is also possible that a bug in Landslide itself may produce a misleading error report. We expect you to protect yourself by responsibly allocating time between Landslide's bug reports and working on the class projects normally. It is expected that participation in this study will require from 2 to 8 hours of active work, depending on bug-finding results.
\\

\noindent {\bf Benefits.}
Because we are testing your code with a more powerful testing tool than is normally distributed with the project, we hope you will be able to fix more concurrency bugs, potentially improving the quality of your submitted projects and resulting in a higher grade.

@@

During this study we will collect personally identifiable information from you as follows. When we run Landslide on your code, we will record the same bug reports we distribute to you, as well as snapshots of your code at the time the bug was found.
We will also collect your answers to the survey, and in this case we will also keep whatever you write confidential from the OS course staff at your university.
%We will also collect paper surveys which you will fill out while using Landslide.
Carnegie Mellon may be required to disclose personally identifiable information as required by law, regulation, subpoena or court order.
%Otherwise, we will protect your confidentiality as follows:
%
%\begin{itemize}
%	\item Bug reports and code snapshots will be stored on CMU computers accessible only to Ben Blum and Garth Gibson.
%	%\item Paper surveys will be stored in a locked filing cabinet accessible only to Ben Blum and Garth Gibson.
%	\item Within one semester after the study, we will destroy all personally identifying information, keeping only anonymized and aggregate results.
%	%\item Professor Eckhardt will have access to study data only after final semester grades are submitted. Other members of course staff will never have access to study data.
%		%Course staff may, however, use Landslide on your final submitted code on their own.
%		%Course staff will also not have access to Landslide to grade your final submission.
%\end{itemize}
%
%\noindent {\bf FALL 2014 NOTE}: This semester, Landslide's automatic data collection is not implemented. We will rely on you to supply commands issued and time spent in the survey section, and to submit Landslide's bug reports and snapshots of your code in a tarball of your workspace.

\section{Your Rights}
There is no coercion or deception associated with this study.
Your participation is voluntary.
You must be 18 years of age or older to participate.
You are free to stop your participation at any point; likewise, the Principal Investigator may at their discretion remove you from the study.
Refusal to participate or discontinued participation in the study will not result in any penalty or loss of benefits or rights to which you might otherwise be entitled.
Your participation or lack thereof will have no impact in your \classname~class grade, except as it might (hopefully) help you write better code.
\\

\noindent If you have any questions about this study, desire additional information, or wish to withdraw
your participation please contact the Principal Investigator by mail, phone or email.
If you have questions pertaining to your rights as a research participant,
or to report concerns about this study, you should contact the
Office of Research Integrity and Compliance at Carnegie Mellon University,
or the IRB at your own institution.

CMU IRB Email: {\tt irb-review@andrew.cmu.edu}. Phone: 412-268-1901 or 412-268-5460.

Berkeley IRB website: {\tt https://cphs.berkeley.edu/}. Email: {\tt ophs@berkeley.edu}.

@@

\begin{itemize}
	\item {\bf Ben Blum} (Principal Investigator): Email: {\tt bblum@cs.cmu.edu}; Office: GHC 9009; Phone: 412-304-4294
	\item {\bf Garth Gibson} (Faculty Advisor): Email: {\tt garth@cs.cmu.edu}; Office: GHC 9111
	%\item {\bf David Eckhardt} (Course Instructor): Email: {\tt de0u@andrew.cmu.edu}; Office: GHC 7717
	\item {\bf Ion Stoica} (Course Instructor): Email: {\tt istoica@berkeley.edu}; Office: 465 Soda Hall
\end{itemize}

### 2018-01-09 irb/infosheet-uchicago.tex
old cleanup: irb

% TODO for berkeley: CS162
\newcommand\classname{CS 162}
\title{\bf Landslide: Systematic Testing in \classname \\ User Study Information Sheet}
\author{Ben Blum}
\date{}
\maketitle

@@

Berkeley IRB website: {\tt https://cphs.berkeley.edu/}. Email: {\tt ophs@berkeley.edu}.

@@

\begin{itemize}
	\item {\bf Ben Blum} (Principal Investigator): Email: {\tt bblum@cs.cmu.edu}; Office: GHC 9009; Phone: 412-304-4294
	\item {\bf Garth Gibson} (Faculty Advisor): Email: {\tt garth@cs.cmu.edu}; Office: GHC 9111
	%\item {\bf David Eckhardt} (Course Instructor): Email: {\tt de0u@andrew.cmu.edu}; Office: GHC 7717
	\item {\bf Ion Stoica} (Course Instructor): Email: {\tt istoica@berkeley.edu}; Office: 465 Soda Hall
\end{itemize}

>>>>

% TODO for berkeley: CS162
\newcommand\classname{CS 230}
\title{\bf Landslide: Systematic Testing in \classname \\ User Study Information Sheet}
\author{Ben Blum}
\date{}
\maketitle

@@

University of Chicago IRB website: {\tt https://sbsirb.uchicago.edu/}

@@

\begin{itemize}
	\item {\bf Ben Blum} (Principal Investigator): Email: {\tt bblum@cs.cmu.edu}; Office: GHC 9009; Phone: 412-304-4294
	\item {\bf Garth Gibson} (Faculty Advisor): Email: {\tt garth@cs.cmu.edu}; Office: GHC 9111
	%\item {\bf David Eckhardt} (Course Instructor): Email: {\tt de0u@andrew.cmu.edu}; Office: GHC 7717
	\item {\bf Haryadi Gunawi} (Course Instructor): Email: {\tt haryadi@cs.uchicago.edu}; Office: Ryerson Hall 259
\end{itemize}

### 2018-01-09 irb/landslide-guide-p2.tex
old cleanup: irb

\begin{enumerate}
	\item Clone the repository - {\tt git clone https://github.com/bblum/landslide.git} - this will be your workspace.
	\item Run {\tt ./p2-setup.sh PATH}, where {\tt PATH} is the absolute path to your p2 implementation.
		\begin{itemize}
			\item This command will import your p2 into {\tt ./pebsim/p2-basecode/} and then attempt to build it.
				Whenever you update your p2 code, please do so in its original {\tt PATH}
				and then run {\tt p2-setup.sh} again.
			\item {\tt PATH} should be the path with {\tt 410kern}, {\tt 410user}, {\tt user/libthread}, etc as subdirectories, not the {\tt user/libthread} directory itself.
		\end{itemize}
	\item Run {\tt ./landslide OPTIONS} to run tests with Landslide, for various values of {\tt OPTIONS}:
		\begin{itemize}
			\item Use ./landslide -h to view command line options. The most important ones are -t , max testing
time, and -p , which test program to run.
			\item Landslide's bug reports will show up as HTML files.
				\begin{itemize}
					\item If you are using a cluster machine in person, you can view them by pointing a browser to \\
						{\tt file:///PATH/TO/landslide/FILENAME.html}
					\item For remote usage, move the html file to {\tt ~/www} in your AFS, and view it at \\
						{\tt http://www.contrib.andrew.cmu.edu/~YOUR\_ANDREWID/FILENAME.html}.
						Note the www in the URL is mandatory;
						note also that this will allow the world to see it,
						so be careful to clean up any traces in {\tt ~/www} when you're done!
				\end{itemize}
			\item Suggested test configurations to run are as follows.
				You can, of course, change the time limits or test programs as you see fit.
				For the longer-running configurations,
				we recommend running them inside of a {\tt screen} or {\tt tmux} session.
				\begin{itemize}
					\item \texttt{./landslide -t 30m -p thr\_exit\_join}
					\item \texttt{./landslide -t 30m -p mutex\_test}
					\item \texttt{./landslide -t 30m -p paradise\_lost}
					\item \texttt{./landslide -t 30m -p broadcast\_test}
					\item \texttt{./landslide -t 30m -p paraguay}
					\item \texttt{./landslide -t 30m -p rwlock\_downgrade\_read\_test}
						\\
					\item \texttt{./landslide -t 3h -p thr\_exit\_join}
					\item \texttt{./landslide -t 3h -p mutex\_test}
					\item \texttt{./landslide -t 3h -p paradise\_lost}
					\item \texttt{./landslide -t 3h -p broadcast\_test}
					\item \texttt{./landslide -t 3h -p paraguay}
					\item \texttt{./landslide -t 3h -p rwlock\_downgrade\_read\_test}
						\\
					\item \texttt{./landslide -t 12h -p thr\_exit\_join}
					\item \texttt{./landslide -t 12h -p mutex\_test}
					\item \texttt{./landslide -t 12h -p paradise\_lost}
					\item \texttt{./landslide -t 12h -p broadcast\_test}
					\item \texttt{./landslide -t 12h -p paraguay}
					\item \texttt{./landslide -t 12h -p rwlock\_downgrade\_read\_test}
				\end{itemize}
			\item To build your own custom test case for use with Landslide,
				put it in {\tt pebsim/p2-basecode/user/progs}
				and edit the {\tt STUDENTTESTS} line in {\tt pebsim/p2-basecode/config-incomplete.mk}
				(note: NOT {\tt config.mk}; the setup script auto-generates that file).
				Then run {\tt ./p2-setup.sh} again.
		\end{itemize}
	\item After fixing any found bugs, re-run Landslide with the same test options to confirm that your fix works.
\end{enumerate}

>>>>

\begin{enumerate}
	\item Clone the repository - {\tt git clone https://github.com/bblum/landslide.git} - this will be your workspace.
	\item Run {\tt ./p2-setup.sh PATH}, where {\tt PATH} is the absolute path to your p2 implementation.
		\begin{itemize}
			\item This command will import your p2 into {\tt ./pebsim/p2-basecode/} and then attempt to build it.
				Whenever you update your p2 code, please do so in its original {\tt PATH}
				and then run {\tt p2-setup.sh} again.
			\item {\tt PATH} should be the path with {\tt 410kern}, {\tt 410user}, {\tt user/libthread}, etc as subdirectories, not the {\tt user/libthread} directory itself.
		\end{itemize}
	\item Run {\tt ./landslide OPTIONS} to run tests with Landslide, for various values of {\tt OPTIONS}:
		\begin{enumerate}
			\item Use ./landslide -h to view command line options. The most important ones are -t , max testing
time, and -p , which test program to run.
			\item Landslide's bug reports will show up as HTML files.
				\begin{itemize}
					\item If you are using a cluster machine in person, you can view them by pointing a browser to \\
						{\tt file:///PATH/TO/landslide/FILENAME.html}
					\item For remote usage, move the html file to {\tt ~/www} in your AFS, and view it at \\
						{\tt http://www.contrib.andrew.cmu.edu/~YOUR\_ANDREWID/FILENAME.html}.
						Note the www in the URL is mandatory;
						note also that this will allow the world to see it,
						so be careful to clean up any traces in {\tt ~/www} when you're done!
				\end{itemize}
			\item Suggested test configurations to run are as follows.
				You can, of course, change the time limits or test programs as you see fit.
				For the longer-running configurations,
				we recommend running them inside of a {\tt screen} or {\tt tmux} session.
				\begin{itemize}
					\item \texttt{./landslide -t 30m -p thr\_exit\_join}
					\item \texttt{./landslide -t 30m -p mutex\_test}
					\item \texttt{./landslide -t 30m -p paradise\_lost}
					\item \texttt{./landslide -t 30m -p broadcast\_test}
					\item \texttt{./landslide -t 30m -p paraguay}
					\item \texttt{./landslide -t 30m -p rwlock\_downgrade\_read\_test}
						\\
					\item \texttt{./landslide -t 3h -p thr\_exit\_join}
					\item \texttt{./landslide -t 3h -p mutex\_test}
					\item \texttt{./landslide -t 3h -p paradise\_lost}
					\item \texttt{./landslide -t 3h -p broadcast\_test}
					\item \texttt{./landslide -t 3h -p paraguay}
					\item \texttt{./landslide -t 3h -p rwlock\_downgrade\_read\_test}
						\\
					\item \texttt{./landslide -t 12h -p thr\_exit\_join}
					\item \texttt{./landslide -t 12h -p mutex\_test}
					\item \texttt{./landslide -t 12h -p paradise\_lost}
					\item \texttt{./landslide -t 12h -p broadcast\_test}
					\item \texttt{./landslide -t 12h -p paraguay}
					\item \texttt{./landslide -t 12h -p rwlock\_downgrade\_read\_test}
				\end{itemize}
			\item To build your own custom test case for use with Landslide,
				put it in {\tt pebsim/p2-basecode/user/progs}
				and edit the {\tt STUDENTTESTS} line in {\tt pebsim/p2-basecode/config-incomplete.mk}
				(note: NOT {\tt config.mk}; the setup script auto-generates that file).
				Then run {\tt ./p2-setup.sh} again.
		\end{enumerate}
	\item After fixing any found bugs, re-run Landslide with the same test options to confirm that your fix works.
\end{enumerate}

\noindent {\bf Note on simultaneous Landslides:} Landslide does not support running multiple tests at once;
it needs to create some temporary files to annotate your code, and multiple instances of Landslide can step on each other's toes by clobbering those files.
If you want to try multiple tests at once, simply {\tt git clone} the repository again in a different directory, and run one instance of Landslide in each.
\\
